\chapter{Characterization of Content Delivery Networks on Autonomous System Level}\label{chap:aslevel}

In the last decade content delivery has shifted from the host-centric to the information-centric network (ICN) paradigm.
To enable efficient traffic management, ICN suggests addressing of content.
Addressing content instead of physical hosts allows utilizing local resources.
To enable addressing, ICN implements naming of information (or content) with unique identifiers.
This allows caching content in the network on available storage on routers.
Since the tree-like structure of the routers unfolds on the path to the end users, the replication of the content scales with its demand.

%To deliver content, it has to be transported from storage resources to clients that consume the content.
%The two most important content delivery concepts in the Internet are peer-to-peer (P2P) networks and content delivery networks (CDNs).
While in the past a large fraction of the total Internet traffic was carried by peer-to-peer (P2P) networks \cite{Cisc09}, the largest fraction of Internet traffic is now carried by content delivery networks (CDNs) \cite{cisco2016}, which follow the ICN paradigm.
%In 2015, 61\% of all Internet video was carried by CDNs \cite{cisco2016}.

%\reffig{fig:aslevel:p2pcdn} shows the AS topology for a P2P network, and a CDN.
%While P2P networks work according to the host-to-host paradigm, CDNs
In case of P2P networks, peers contribute to the delivery of content by serving chunks of data.
To enable exchange of data, a tracker keeps track of the peers sharing chunks of a file.
For every file which is exchanged within the network, P2P networks form a separate, mesh-based overlay.
P2P networks are still responsible for a large fraction of Internet traffic.
%produces transit costs for ISPs
%intro and problem
% The performance evaluation of mechanisms that optimize content delivery requires a thorough knowledge of the nature of current content delivery networks.
% Such knowledge is required to reflect the characteristics of real-world networks and to define models, parameters and relevant scenarios for performance evaluation.
% This ensures that the results derived from performance analysis give meaningful insights for real-world scenarios.
%Dependent on the route the content takes The delivery of content produces costs
%The Internet is a network of autonomous systems.
%The scalability of the Internet is achieved by topological addressing.
%ISPs acquire transit providers to be connected to remote parts of the Internet or agree on peering relationships to exchange data without money flow.
In CDNs the content provided by a content provider is replicated to caches deployed in data-centers in many different geographic locations.
Content requests are redirected to the closest cache location that can serve the content.
%The vast amount of traffic causes high costs for ISPs, who need to provide appropriate transport infrastructure and pay transit fees incurred.

Autonomous systems (ASs) are individual parts of the Internet controlled of one or more network operators on behalf of a single administrative entity.
To be connected to remote ASs in the Internet, ISPs acquire transit providers or agree on peering relationships.
Transit provider charge transit fees for inter-domain traffic, which is traffic routed to different ASs.
The problem is that a high amount of costly inter-domain traffic can be caused by both content delivery concepts, P2P and CDN.

The inter-domain traffic caused by P2P networks is especially high, if the exchange of data among peers is uncoordinated.
The traffic originating from CDNs is highly asymmetric and thus also produces a large amount of inter-domain traffic \cite{labovitz2010internet}.
%Especially ISPs providing access to many end users have problems to deal with the huge amount of traffic originating from CDNs.
Reducing the traffic carried by CDNs and the load put on ISP networks has high potential to reduce energy consumption and cost for content delivery and transit.
In order to develop traffic management mechanisms, aiming to reduce inter-domain traffic and to optimize content delivery, it is crucial to understand the current situation of CDNs and the number and distribution of available resources.
%The performance of CDNs highly depends on the available resources and the number of consumers.

%The interaction of such applications with the network and other players, e.g. cloud providers, are usually not considered by the application developers.
%In peer-to-peer networks

% overview
% in this chapter, ...

In this chapter, we show the principles and recent developments of content delivery networks and characterize their resources on AS level by performing and evaluating distributed measurements.
The models derived are used for traffic characterization and to develop optimization strategies to reduce inter-domain traffic and transit costs.
%and characterize the topology of autonomous systems.

%In peer-to-peer networks peers serve and request chunks of content at the same time, hence peers are also the resources for content delivery.

%In content delivery networks the resources are content caches that run in data centers. To get content even closer to users caches can also be installed at the last mile or on customer premise equipment in home networks.

% details, figure
In order to characterize P2P networks on AS level, we analyze a measurement study and identify the number of peers per swarm available in each AS and investigate the performance of different peer selection strategies.
% we consider + metrics
As key performance indicators we determine the traffic volume and the traffic costs of ISPs.

For the characterization of CDNs on AS level, a distributed measurement architecture is necessary to identify the server resources, due to the location based server assignment of CDNs.
%While peers in P2P networks can easily be identified by probing trackers, the cache resources of CDNs can only be determined by probing the CDN from different locations.
Typically, distributed measurement platforms such as PlanetLab are used for that purpose.
The problem is that these measurement platforms may not reflect the perspective as consumer, since they are hosted in National Research and Education Networks (NRENs) and not in ISP networks.
We compare the capabilities of a crowdsourcing platform and a PlanetLab testbed for distributed active measurements of CDNs.
%In order to characterize the distribution of resources in content delivery networks, simple tracking is not possible, since no publicly available registers exist.

Recent approaches \cite{valancius2009greening} suggest to use resources on customer premise equipment (CPE) such as home routers or network attached storage to support content delivery while saving energy.
The potential of such peer assisted content delivery approaches depends on the number of subscribers in the ISPs network.
To get a global view on the number of resources available in each AS, we evaluate the Internet Census Dataset, which contains a complete scan of the IP address range.

%We compare a measurement study
% contribution
% The contribution of this chapter is the following:
% \begin{enumerate}
% \item We determine the distribution of P2P and CDN resources on ASs.
% \item We develop and evaluate optimization strategies for P2P networks.
% \item We evaluate the Internet Census Dataset and model the distribution of IP-addresses on ASs.
% \end{enumerate}

The models derived from the measurement results are used for performance analysis and optimization of content delivery mechanisms.
In particular the models serve as input for the optimization strategies for peer selection and the performance evaluation of hierarchical CDNs in realistic parameter studies in \refchap{chap:hierarchical}.
%In addition our results show that the size of ISP in terms of subscriber is highly heterogeneous, showing that more than 85\% of the IPs are active in only 1\% of the autonomous systems and that the 10 largest autonomous systems already contain 30\% of the active IPs.
%100 largest ISPs have 2/3 of active IPs

The content from this chapter is published in \cite{burger2012profit,burger2014vantage,burger2016hierarchical}.
\refsec{sec:aslevel:background} describes the evolution and structure of content delivery networks.
We present measurements and models of CDNs in \refsec{sec:aslevel:measurements}.
In \refsec{sec:aslevel:crowd} two approaches for distributed active measurements are compared towards their capability to probe servers in CDNs and the global CDN of YouTube is characterized.
%The evaluation of the Internet census dataset is presented in \refsec{sec:aslevel:census}.
The applied methodology to characterize P2P traffic and to estimate its transit costs is described in \refsec{sec:aslevel:p2p}.
We discuss lessons learned in \refsec{sec:aslevel:lessons_learned}.

\input{aslevel/background/background}
\input{aslevel/measurements/measurements}
\input{aslevel/crowd/crowd}
\input{aslevel/p2p/p2p}
%\input{aslevel/census/census}
\input{aslevel/lessons_learned/lessons_learned}
